\documentclass[12pt,oneside]{report}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{preambule_2020_overleaf}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\portrait
%\paysage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%À modifier !!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!
\newcommand{\classe}{Euro section 2nde}
\newcommand{\anneescol}{School year 2019-2020}

%entête classique

\fancypagestyle{garde_tete}{% 
%\fancyhead[C]{\small\textbf{\seconde} \hfill \small \textbf{Année 2015-2016}}
\renewcommand{\headrulewidth}{0cm}}

\newcommand{\tete}{
\thispagestyle{garde_tete}
\chapitre{Comments on your recordings}
\noindent 
\vspace{-1em}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\tikzset{domaine/.style 2 args={domain=#1:#2}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%
%% DEBUT DU DOCUMENT %%
%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
%\selectlanguage{english}
\selectlanguage{french}
\setlength\parindent{0mm}
\tete 		%entête classique

\renewcommand \footrulewidth{0.2pt}%
\renewcommand \headrulewidth{0pt}%
\pagestyle{fancy}
\fancyhf{}
\pieddepage{\classe}{\thepage / \pageref{LastPage}}{\anneescol}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{spacing}{1.2}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{General comments}

$\star$ I thank all the students who did the job during the lockdown. It wasn't that easy for you to stay motivated.

And most of you really managed to do it!

You can be proud of you.

$\star$ As I've put some corrections in your scripts, the following comments are on words/expressions you mispronounced.

Sometimes you don't put the stress in the right place in the word you are pronouncing.

$\star$ To check the pronunciation, I remind you that you have many options.

I've put some useful links in this webmix:

\url{https://www.symbaloo.com/mix/eurosectiondomt}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\section{First podcasts}

\subsection*{Théophile \& Timothé}

talk, quadrilateral, future, rhombus, with, parallelogram

perpendicular, bisecting, measure, finally, trapezoid


\subsection*{Corentin \& Clément}

\color{blue}
I haven't found your first podcast
\color{black}


\subsection*{Laure \& Camille}

\color{blue}
I haven't found your first podcast
\color{black}


\subsection*{Azza}

dilatation

\color{blue}
Your accent and your pronunciation are so good, Azza!

I'm just impressed!
\color{black}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\section{Challenge of the holiday}

\subsection*{Max}

amount, area, objective

\color{blue}
Your pronunciation is almost perfect! Great job, Max!
\color{black}

\subsection*{Layla}

amount, huge, separate, all, area

\color{blue}
You did a great job, Layla!
\color{black}


\subsection*{Corentin}

amount, enough, Germany

You did a great job, Corentin!

\subsection*{Laure \& Camille}

talking, amount, recycling, pourcentage, could, able

\color{blue}
You did a great job, Laure \& Camille!
\color{black}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Class assistant presentations}



\subsection*{Layla}

talk, primary, scientific, brightness, composed, fusion

\subsection*{Eva}

talk, primary, temperature, chimical, hydrogen

\subsection*{Naïm}

\color{blue}
controversial (instead of controversed)
\color{black}

aren't, bacteria

\color{blue}
You've got a very good accent, Naïm!
\color{black}

\subsection*{Théo}


quantum, probability, mathematically, defined

\color{blue}
You've got a good accent, Théo!
\color{black}


\subsection*{Victoria}

\color{blue}
physics instead of physical
\color{black}

method, pyramid

\color{blue}
You've got a good accent, Victoria!
\color{black}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Weeks 5 \& 6}

\subsection*{Lucie F. \& Maïlyne}

\color{blue}
I haven't got your podcast.
\color{black}

\subsection*{Laure \& Camille A.}

climate, atmosphere

\color{blue}
Thanks for your work!
\color{black}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Weeks 8 \& 9}




%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{spacing}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%
%% FIN DU DOCUMENT %%
%%%%%%%%%%%%%%%%%%%%%
\end{document}