\documentclass[12pt,oneside]{report}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{preambule_2020_overleaf}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\portrait
%\paysage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%À modifier !!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!
\newcommand{\classe}{Euro section 1ère}
\newcommand{\anneescol}{School year 2019-2020}

%entête classique

\fancypagestyle{garde_tete}{% 
%\fancyhead[C]{\small\textbf{\seconde} \hfill \small \textbf{Année 2015-2016}}
\renewcommand{\headrulewidth}{0cm}}

\newcommand{\tete}{
\thispagestyle{garde_tete}
\chapitre{Comments on your recordings}
\noindent 
\vspace{-1em}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\tikzset{domaine/.style 2 args={domain=#1:#2}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%
%% DEBUT DU DOCUMENT %%
%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
\selectlanguage{english}
%\selectlanguage{french}
\setlength\parindent{0mm}
\tete 		%entête classique

\renewcommand \footrulewidth{0.2pt}%
\renewcommand \headrulewidth{0pt}%
\pagestyle{fancy}
\fancyhf{}
\pieddepage{\classe}{\thepage / \pageref{LastPage}}{\anneescol}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{spacing}{1.2}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{General comments}

$\star$ I thank all the students who did the job during the lockdown. It wasn't that easy for you to stay motivated.

And most of you really managed to do it!

You can be proud of you.

$\star$ As I've put some corrections in your scripts, the following comments are on words/expressions you mispronounced.

Sometimes you don't put the stress in the right place in the word you are pronouncing.

$\star$ To check the pronunciation, I remind you that you have many options.

I've put some useful links in this webmix:

\url{https://www.symbaloo.com/mix/eurosectiondomt}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\section{Mathematical podcasts}


\subsection*{Léna P.}

basis, circle, complete, place, aren't, multiples, Euclidean

\color{blue}
You did a long format video. It must have been a long work.

Thanks for it!
\color{black}

\subsection*{Oscar}

mathematical, spreadsheet, answer, immediately, amount, item, instead

\color{blue}
You have really improved your pronunciation this year!

I'm impressed!

You did a long format podcast. It must have been a long work.

Thanks for it!
\color{black}


\subsection*{Thomas \& Lény}

scientist, favorite, product, ultimately

\color{blue}
You did a really great job. It's a pity\dots it's the only one!
\color{black}

\subsection*{Gabin}

\color{blue}
You've got a very good accent. Thanks for your job!

Everything is perfect!
\color{black}

\subsection*{Inès}

\color{blue}
dynamic instead of dynamical
\color{black}

variable, dynamic, $g(x)$, machine, above, metaphor, base, typically, instead, according, calculus 

\color{blue}
You did a long format podcast. It must have been a long work.

Thanks for it!

You did a really great job!
\color{black}

\subsection*{Thomas L. \& Thibault}

\color{blue}
I haven't found your podcast.
\color{black}

\subsection*{Léo-Pol, Mathieu, Léo \& Maxime}

\color{blue}
I haven't found your podcast.
\color{black}

\subsection*{Margaux \& Léna D.}

\color{blue}
I haven't found your podcast.
\color{black}

\subsection*{Émilie, Perrine \& Justine}

determine, $\Delta$, parentheses, minus, $x$, $f'(x)$, interval, symbol

\color{blue}
Thanks for your job!
\color{black}

\subsection*{Achille}

noted, natural, $\mathbb{R}$, previous, abscissa

\color{blue}
Thanks for your job!
\color{black}

\subsection*{Niels \& Barbara}

60, 40, 30, 70. Niels!!!!!!

\color{blue}
Thanks for your work. You made a great video\dots even if it's a bit short.
\color{black}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\section{Challenge of the holiday}

\subsection*{Mathieu}

\color{blue}
I haven't found your podcast.
\color{black}

\subsection*{Justine}

tackled

\color{blue}
Your part is almost perfect!

Thanks for your work! It's a great one.
\color{black}

\subsection*{Marius}

interesting, amount, waste, New Zealand, tackled, answer, surprised

\color{blue}
Thanks for your work!
\color{black}

\subsection*{Tom}

thought, little, highest, $a$, $b$, $c$, urban

\color{blue}
You did a great job! Thanks for it!
\color{black}

\subsection*{Margaux}

\color{blue}
It's just perfect! I'm impressed by your pronunciation and by your work!

You did a much bigger work than the one asked to do.

And again thank your father!
\color{black}

\subsection*{Léna P.}

manufacturer, recycled, bit, phrase, answer, circular, rather, breaks, recycled, repaired, assuming, ignoring, soon, now

\color{blue}
You did a really great job!

You did a much bigger work than the one asked to do.
\color{black}

\subsection*{Oscar}

\color{blue}
climate instead of \og climat \fg{} 
\color{black}

cyclones, nuclear

\color{blue}
It's a ggod idea to do it like that\dots even if\dots it's quite a serious subject\dots ;)
\color{black}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Class assistant presentations}

\subsection*{Inès}

finally, declaration

\color{blue}
It's a great job! Thanks for it!

It's almost perfect!
\color{black}

\subsection*{Héléna}

stimuli, ideal

\color{blue}
It's almost perfect and very interesting.

You've got a very good pronunciation!

You did a great work!
\color{black}

\subsection*{Léna D.}

\color{blue}
\og I spent time\fg{} instead of \og I past time \fg{} 
\color{black}

However, even

\color{blue}
Thanks for your work!

I think you've improved your pronunciation this year.
\color{black}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Weeks 5 \& 6}

\subsection*{Margaux}

\color{blue}
I've nothing to say except\dots it's just perfect!!!!!!!!!!!!!!!

And you've got a great idea to put it online. 

\videoyoutube{https://www.youtube.com/watch?v=QZRqNMPMnzc}

If you don't want to get a watermark on the videos you'll create you can use OpenShot Video Editor (\url{https://www.openshot.org/}) to do it which is an free and open-source software you can use with Linux, Mac or Windows.
\color{black}

\subsection*{Léna P.}

Does, creater, mathematician, mathematical, overcrowding, enough, isolation, infinity, finite

\color{blue}
Thanks for your work!

You spent a lot of time for these podcasts. I can see it.

Thanks again!
\color{black}

\subsection*{Mathieu}

surface, temperature

\color{blue}
You did a great job!

I think you've improved your pronunciation, or at least, you were very careful of it during your recording.

Thanks for it!!
\color{black}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Newspaper articles}





%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{spacing}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%
%% FIN DU DOCUMENT %%
%%%%%%%%%%%%%%%%%%%%%
\end{document}