\documentclass[12pt,oneside]{report}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{preambule_2020_overleaf}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\portrait
%\paysage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%À modifier !!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!
\newcommand{\classe}{Euro section 2nde}
\newcommand{\anneescol}{School year 2019-2020}

%entête classique

\fancypagestyle{garde_tete}{% 
%\fancyhead[C]{\small\textbf{\seconde} \hfill \small \textbf{Année 2015-2016}}
\renewcommand{\headrulewidth}{0cm}}

\newcommand{\tete}{
\thispagestyle{garde_tete}
\chapitre{Comments on your recordings}
\noindent 
\vspace{-1em}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\tikzset{domaine/.style 2 args={domain=#1:#2}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%
%% DEBUT DU DOCUMENT %%
%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
\selectlanguage{english}
%\selectlanguage{french}
\setlength\parindent{0mm}
\tete 		%entête classique

\renewcommand \footrulewidth{0.2pt}%
\renewcommand \headrulewidth{0pt}%
\pagestyle{fancy}
\fancyhf{}
\pieddepage{\classe}{\thepage / \pageref{LastPage}}{\anneescol}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{spacing}{1.2}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{General comments}

$\star$ I thank all the students who did the job during the lockdown. It wasn't that easy for you to stay motivated.

And most of you really managed to do it!

You can be proud of you.

$\star$ As I've put some corrections in your scripts, the following comments are on words/expressions you mispronounced.

Sometimes you don't put the stress in the right place in the word you are pronouncing.

$\star$ To check the pronunciation, I remind you that you have many options.

I've put some useful links in this webmix:

\url{https://www.symbaloo.com/mix/eurosectiondomt}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Maths \& Arts or Maths \& Games}

\subsection*{Team \# 1 : Tom, Flavie M. \& Inès}

counting, Egyptian, famous

\color{blue}
You did a great work!

You speak really clearly.

Thanks for your work!
\color{black}


\subsection*{Team \# 2 : Gaël \& Ricardo}

Mathematical, fundamental, mathematics, such, matrices, area, advanced, idea, allows, also, algorithmic, algorithm

\color{blue}
Thanks for your work!

It should have been easier to show graphics\dots with a video ;)
\color{black}

\subsection*{Team \# 3 : Flavie J., Dilara \& Julie}

periodic, finite

\color{blue}
It's almost perfect!

Thanks for your work.

You all three have a really good accent and clear pronunciation!

I'm impressed!
\color{black}

\subsection*{Team \# 4 : Lucas, Angéline \& Noé}

frequency, duration, symbolized, could, categorization, table, illustrate, relative, even, octave, ratio

\color{blue}
There's a mistake: you should have written $\sqrt[12]{2}$ instead of $12\times \sqrt{2}$. These numbers are not the same ones.

You really made a great presentation!

Thanks Angéline! ;)

Thanks for your work!
\color{black}

\subsection*{Team \# 5 : Titouan, Hugo \& Émilien}

architecture, Egyptian, measure, decimal, method, theory, also, $a$, around, divine, architect, mathematically, potential, hyperbolic, lowest, perimeter, attributed, allowed, various, material, althought, largest, determined, cubic, identify, since, evolved, total, surface, possible, $y$-axis, diagram, could, calculation

\color{blue}
As you can see, you've got many words' pronunciation to check.

But you did a great job!

Your presentation is a long one, so\dots you are more likely to make mistakes than your clasmates.
\color{black}

\subsection*{Team \# 6 : Thibaut \& Kyrian}

\color{blue}

\color{black}

\subsection*{Team \# 7 : Clara \& Maëlyss}

Headcount, euros, think, profitability

\color{blue}
You made a great video even if it's quite simple! 

It easier for the listener to follow you.

Thanks for it!
\color{black}

\subsection*{Team \# 8 : Bilal, Samuel, Redwan \& Youssou}

\color{blue}

\color{black}

\subsection*{Team \# 9 : Antoine, Mathieu, Sallé \& Victor}

\color{blue}

\color{black}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%



\section{Challenge of the holiday}

\subsection*{Titouan}

rubbish, amount, huge, Germany, think, later, area, waste

\color{blue}
It's a good job!

Thanks for it!

To improve your pronunciation, you can listen to your record and compare with the original one.
\color{black}

\subsection*{Maëlyss}

rubbish, separate, country, 

\color{blue}
It's a great work, Maëlyss! Thanks for it!

Your accent and your pronunciation are almost perfect!
\color{black}

\subsection*{Inès}

area, develop, circular, highest, media

\color{blue}
You did a really great job!

Your accent and your pronunciation are almost perfect!
\color{black}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%



\section{Weeks 5 \& 6}

\subsection*{Clara \& Maëlyss}

receive, climate, return, atmosphere, pandemic

\color{blue}
Thanks for your work!

It's a great idea to create an interview!

You spoke very clearly.
\color{black}

\subsection*{Gaël}

\color{blue}
I haven't got your podcast.
\color{black}

\subsection*{Titouan}

answered, proud, rule, squared, neighbour, structure

\color{blue}
You did a great work!

Thanks for it.
\color{black}

\subsection*{Kyrian}

scientific, written, would, phenomena, gigaton, reserve, whole, think

\color{blue}
It's a great work\dots even if you've got some words' pronunciation to check.

And don't worry for your French accent.

If you can keep it. Just be careful of the sound and the stress.
\color{black}

\subsection*{Flavie M.}

\color{blue}
I haven't got your podcast.
\color{black}

\subsection*{Inès}

NASA, according, catastrophic, experiment, America, temperature, raise, 

\color{blue}
Again, your pronunciation is almost perfect, even if you've got some words to check.

Thanks for your work!
\color{black}

\subsection*{Ricardo}

hate

\color{blue}
You did a great work! Thanks for it.

Your pronunciation is perfect!
\color{black}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Newspaper articles}


\subsection*{Angéline, Noé \& Lucas}

Your podcast: I'm waiting for it\dots

\color{blue}
It's a so nice looking work! Thanks for it!
\color{black}

\subsection*{Julie, Dilara \& Flavie J.}

Your podcast: I'm waiting for it\dots

\color{blue}
It's a so nice looking work! Thanks for it!
\color{black}

\subsection*{Clara \& Maëlyss}

Your podcast: related

\color{blue}
You did a really great job these past few days!

I'm impressed! Thanks for it !
\color{black}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{spacing}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%
%% FIN DU DOCUMENT %%
%%%%%%%%%%%%%%%%%%%%%
\end{document}